\vspace{-2cm} Inference on the Effects of Observed Features \\ in Latent Space Models for Networks

### 2016-09-01 manuscript.tex
finished prior section

To derive our scaling rule, we follow the thought experiment of a one-dimensional latent space $\mathbf{z}$ with a dyadic covariate $\mathbf{x}$. If we assume that the $\mathbf{z}$ are independent and distributed $\mathcal{N}(0,\sigma^2)$, it is straightforward to derive the distribution of $|z_i - z_j|$.\footnote{The assumption that $\mathbf{z} \sim \mathcal{N}(0,\sigma^2$) is consistent with $\mathbf{z}$ being drawn from the prior that is conventionally used in the LSM.} Since it is a special case of a ``normal difference distribution'', we know that $z_i - z_j \sim \mathcal{N}(0,2\sigma^2)$ \citep{devore2012}. The normality of $z_i - z_j$ implies that $|z_i - z_j|$ has a folded normal distribution \citep{leone1961}. Following from this result, we know that the variance of  $|z_i - z_j|$ is $$\sigma^2(2-4/\pi). $$ Let $\theta^2$ be the empirical variance of $\mathbf{x}$. Then the variance in the linear predictor is $\beta^2\theta^2$. Given an estimate $\hat{\beta}$, we can set the variance of the latent space prior to a multiple of $\hat{\beta}^2\theta^2/(2-4/\pi)$ in order to tune the prior to avoid replicating the linear predictor via the distances between latent coordinates.

\subsection{Simulation Study}

>>>>

Our scaling rule is expressed as the prior variance for the latent positions, denoted $\eta^2$. We focus on a one-dimensional latent space $\mathbf{z}$ with a single dyadic covariate $\mathbf{x}$. The rule we derive generalizes naturally to more than one dimension, as the prior variance for each dimension could simply be set to $\eta^2/d$ where $d$ is the number of dimensions.  If we assume that the $\mathbf{z}$ are independent and distributed $\mathcal{N}(0,\sigma^2)$, it is straightforward to derive the distribution of $|z_i - z_j|$.\footnote{The assumption that $\mathbf{z} \sim \mathcal{N}(0,\sigma^2$) is consistent with $\mathbf{z}$ being drawn from the prior that is conventionally used in the LSM.} Since it is a special case of a ``normal difference distribution'', we know that $z_i - z_j \sim \mathcal{N}(0,2\sigma^2)$ \citep{devore2012}. The normality of $z_i - z_j$ implies that $|z_i - z_j|$ has a folded normal distribution \citep{leone1961}. Following from this result, we know that the variance of  $|z_i - z_j|$ is $\sigma^2(2-4/\pi)$.  Let $\theta^2$ be the empirical variance of $\mathbf{x}$. Then the variance in the linear predictor is $\beta^2\theta^2$. Given an estimate $\hat{\beta}$, we can set the variance of the latent position prior to $$\eta^2=\hat{\beta}^2\theta^2/(2-4/\pi).$$  This prior would actively penalize latent distance distributions that match or exceed the variance of the observed linear predictor. 
\subsection{Simulation Study}
